User Guide for KvApp

### 2022-03-27 KvApp_guide.Rmd
Getting started

---
title: "User Guide for K~v~App"
author: "Haedong Kim"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

K~v~App

Although K~v~App is developed in MATLAB, it does not require MATLAB installed on the machine. Instead, running `MyAppInstaller_web` will install the packaged application and MATLAB Runtime from the Internet, which enables the application to run without MATLAB. Your computer needs to be connected to the Internet to complete the installation. You will get the error message below if the right version of MATLAB Runtime.
![]()

>>>>

---
title: "User Guide for KvApp"
author: "Haedong Kim"
date: "`r Sys.Date()`"
output: pdf_document
---

@@

There are four associated files as shown in Figure 1 below: `KvAppBeta`, `MyAppInstaller_mcr`, `MyAppInstaller_web`, and `splash`.

![Consisting files of the applications.](KvApp_guide_img/folder_struct.png){width=50%}

`KvAppBeta` is the file that runs the application, but you will get the error message in Figure 2 if the correct version of MATLAB is not installed on the machine.

![Error message when the right version of MATLAB is not installed on the target machine.](KvApp_guide_img/runtime_error.png){width=50%}

`MyAppInstaller_web` will install the packaged application and MATLAB Runtime from the Internet, which enables the application to run without having MATLAB installed. Your computer needs to be connected to the Internet to complete the installation. If the Internet connection is not available, `MyAppInstaller_mcr` will install the necessary programs locally. A few screenshots below show the installation process.

![](KvApp_guide_img/install1.png){width=50%} ![](KvApp_guide_img/install4.png){width=50%}
![](KvApp_guide_img/install5.png){width=50%} ![](KvApp_guide_img/install6.png){width=50%}

The other file `splash` is just an image file for the application icon.
